---
title: "barcc"
output: github_document
---

<!-- README.md is generated from the README.Rmd file. Edit that file for updates -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## THIS PACKGAES IS IN BETA VERION!

The packges will take pre-processed copy of raw baracoda files and mupexi files and illustrate the characteristics of the immunugenic neopeptides. 

## Installation and background

The packges will take pre-processed copy of raw baracoda files and mupexi files and illustrate the characteristics of the immunugenic neopeptides. 
The packgaes works only with murine data, The human data input is in progress ... 

```{r, eval = F}
# install.packages("devtools")
library(devtools)
devtools::install_github("rforbiodatascience/barcc")
```
barcc is built with [tidyverse](https://github.com/tidyverse/tidyverse)  and is required for running 
## required packages 
```{r}
library(tidyverse)
library(readxl)
library(openxlsx)
library(shiny)
library(ggplot2)
library(barcc)
```

# Load data

## Baracoda files
Baracoda files from experiment must be loaded 
```{r}
path_ct26 <- "test_data/barracoda_output_CT26.xlsx"
path_4t1 <- "test_data//barracoda_output_4T1.xlsx"
all_ct26_barracoda_raw <- path_ct26 %>% 
    # function to import all sheets
    excel_sheets() %>% 
    # give names to each sheet
    set_names() %>% 
    # apply read_excel to each sheet, and add the number to the colum sheet
    map_df(~ read_excel(path = path_ct26, sheet = .x), .id = "sheet") 
  
all_4t1_barracoda_raw <- path_4t1 %>% 
    excel_sheets() %>% 
    set_names() %>% 
    map_df(~ read_excel(path = path_4t1, sheet = .x), .id = "sheet")

```

## Mupexi files 
Load all mupexi files and 
```{r}
mupexi_ct26 <- read_xlsx(path = "test_data/ct26_library_mupexi.xlsx") %>% 

mupexi_4t1 <- read_xlsx(path = "test_data/4T1_library_mupexi.xlsx") %>% 
  select(-identifier, -"...1")
```
## PE population info and buffycoat HLA info file
```{r}
sample_info <- read_xlsx(path = "test_data/sample_info.xlsx")
buffycoat.HLA_info <- read_xlsx(path = "test_data/buffycoatHLA_info.xlsx")
```


## Merge all baracoda files 

```{r}
all_barracoda <- full_join(all_ct26_barracoda_raw, all_4t1_barracoda_raw)
```
## Merge mupexi files 

```{r}
all_mupexi <- full_join(mupexi_4t1, mupexi_ct26)
```

# Merge data function
Use merge function to merge baracoda and mupexi files the output is my_data 

```{r}
my_data <- merge_all_data(all_barracoda =  all_barracoda,
                           all_mupexi  = all_mupexi,
                          sample_info = sample_info,
                          buffycoat.HLA_info  = buffycoat.HLA_info)

```

# Clean data function 
with clean data function the varribale is cleaned and reay to import in augment_data fundtion 
```{r}
my_clean_data <- clean_data(my_data)
```

# Augment data 
This function will make new column esimated frequency from the baracaoda screening 

```{r}
my_clean_augment_data <- augment_data(my_clean_data)
```


# Explore data in shiny app 
Tha data can easy be open in a shiny app to explore the responses and the if tehre is and pattern in the immunugenic neoepitopes 
```{r}
Exploring_data_shiny(Plotting_data = my_clean_augment_data )
```





