---
title: "barcc"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The packges will take pre-processed copy of raw baracoda files and mupexi files and illustrate the characteristics of the immunugenic neopeptides. 

## Installation and background

The packges will take pre-processed copy of raw baracoda files and mupexi files and illustrate the characteristics of the immunugenic neopeptides. 
The packgaes can take mouse data as input. 
The human data input is in process ... 

```{r, eval = F}
# install.packages("devtools")
library(devtools)
devtools::install_github("rforbiodatascience/barcc")
```
barcc is built with [tidyverse](https://github.com/tidyverse/tidyverse)  and is required for running 
## required packages 
```{r}
library(tidyverse)
library(readxl)
```


# Load data

## BARRACODA FILES
```{r}
path_ct26 <- "test_data/barracoda_output_CT26.xlsx"
path_4t1 <- "test_data//barracoda_output_4T1.xlsx"
all_ct26_barracoda_raw <- path_ct26 %>% 
    # function to import all sheets
    excel_sheets() %>% 
    # give names to each sheet
    set_names() %>% 
    # apply read_excel to each sheet, and add the number to the colum sheet
    map_df(~ read_excel(path = path_ct26, sheet = .x), .id = "sheet") 
  
all_4t1_barracoda_raw <- path_4t1 %>% 
    excel_sheets() %>% 
    set_names() %>% 
    map_df(~ read_excel(path = path_4t1, sheet = .x), .id = "sheet")

```

## MUPEXI FILES
```{r}
mupexi_ct26 <- read_xlsx(path = "test_data/ct26_library_mupexi.xlsx") %>% 
  # remove extra columns from previous handling
  select(-identifier, -Mut_peptide.y, -Allele) %>% 
  # convert Mut_MHCrank_EL and Expression level to numeric so we can join both files
  mutate(Mut_MHCrank_EL = as.numeric(Mut_MHCrank_EL),
         Expression_Level = as.numeric(Expression_Level))

mupexi_4t1 <- read_xlsx(path = "test_data/4T1_library_mupexi.xlsx") %>% 
  select(-identifier, -"...1")
```
## PE_population_info and buffycoat_HLA_info file
```{r}
sample_info <- read_xlsx(path = "test_data/sample_info.xlsx")
buffycoat.HLA_info <- read_xlsx(path = "test_data/buffycoatHLA_info.xlsx")
```


## merge all baracoda files 

```{r}
all_barracoda <- full_join(all_ct26_barracoda_raw, all_4t1_barracoda_raw)

```
# merge mupexi files 

```{r}
all_mupexi <- full_join(mupexi_4t1, mupexi_ct26) %>% 
    # identifier column to merge with barracoda - HLA_peptidename
    mutate(identifier = paste(HLA_allele, Mut_peptide, sep = "_"))
```


## use merge function to merge baracoda and mupexi files the output is my_data 

```{r}
merge_all_data(baracoda =  all_barracoda ,
                          mupexi  = all_mupexi,
                          sampel_information = sample_info,
                          buffycoat_HLA_information  = buffycoat.HLA_info)

```

## clean data with clean data function 
```{r}
my_clean_data <- clean_data(my_data)
```

## augment data and add the esimated frequency

```{r}
my_clean_augment_data <- augment_data(my_clean_data)
```


## explore data in shiny app 






