---
title: "barcc"
output: github_document
---

<!-- README.md is generated from the README.Rmd file. Edit that file for updates -->

```{r, echo = FALSE, warning=FALSE, message=FALSE,cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  warning=FALSE,
  message=FALSE
)
```

The packges will take pre-processed copy of raw baracoda files and calculate estimated frequency

## Installation and background

The packges will take pre-processed copy of raw baracoda files and mupexi files and illustrate the characteristics of the immunugenic neopeptides. 
The packgaes works only with murine data, The human data input is in progress. 

```{r, eval = F}
# install.packages("devtools")
library(devtools)
devtools::install_github("SRHgroup/barcc")
library(barcc)
```
barcc is built with [tidyverse](https://github.com/tidyverse/tidyverse)  and is required for running.
## required packages 
```{r}
library(tidyverse)
library(readxl)
library(openxlsx)
library(ggplot2)
library(barcc)
library(ggrepel)
library(ggbeeswarm)
library(knitr)
```

## Load data

### Baracoda files
```{r inputs}
# name of fold change file
baracoda_output <- "test_data/fold_change_example_file_new.xlsx"
results_figures_path <- "results/figures/"
results_tables_path <- "results/tabels/"

# if you allready have PE table 
percent_FU <- "test_data/percent_PE_modi.xlsx"
# else follow the guidance and run the function "generate_FU_template_tab" after loading data 

```

### log fold change files 
Load data  
```{r load data}

# load data
my_barrcoda_data <- load_data(data = baracoda_output)
```


## Add percent flourchrome information
generate template
```{r add percent flourchrome}
# iF you want a template run function
generate_FU_template_tab(data = my_barrcoda_data, outfile = "test_data/percent_PE.xlsx")

```


Then change template with corresponding PE
generate template
```{r add load percent flourchrome}
# load file
percent_FU <- "test_data/percent_PE_modi.xlsx"
FU_data <- read.xlsx(percent_FU)
head(FU_data)
```

## responses and estimated frequency
Add column with reponses 

```{r add response column}
my_barrcoda_data <- add_response_by_threshold(data = my_barrcoda_data,
         FC = 2, p_val = 0.001)
my_barrcoda_data %>% group_by(sample,response) %>% tally()
```

Add estimated frequency and normalized estimated frequency

```{r add estimated frequency}
my_barrcoda_data <- estimated_frequency(data = my_barrcoda_data, fluochrome_dat = percent_FU)

my_barrcoda_data %>% select(sample,Peptide,HLA,estimated_frequency, estimated_frequency_normalised_responses)

```

# Time for plotting 
Overall responses 
```{r bar_resp figure, out.width = '80%', warning=FALSE}
p <- barc_resp(data = my_barrcoda_data, est_freq = 'estimated_frequency_normalised_responses')
p
save_figure(plot = p, name = "response_figure" , width = 18 , height = 8)
```


Write output table 
```{r bar_resp figure, out.width = '80%', warning=FALSE}
write.table(my_barrcoda_data, file = "results/tabels/barracoda_output_final.tsv", sep = "\t", quote = F, row.names = F)

```


# done


